The fraction of polar aligned circumbinary disks

### 2025-04-04 src/tex/ms.tex
L580

>>>>

\RR{
    Together, the processes of disk breaking and gravitational instability lead to disks that are less massive and less radially extended. These processes should lower the statistical weight of massive, extended disks and make $f_\text{polar}$ more heavily dependent on narrower disks with small masses (low $j$). The dynamical states of these disks are more strongly dependent on $e_\text{b}$ and evolve to a stable configuration on shorter timescales. Without an underlying binary eccentricity distribution it is difficult to say if $f_\text{polar}$ increases or decreases when these effects are considered. However, the fraction of disks whose lifetimes are shorter than their alignment timescales would be reduced, and we would expect to see fewer disks outside of polar or coplanar configurations. 
}

### 2025-04-04 src/tex/review.tex
L628
L615
L580

\documentclass{letter}
\usepackage{xcolor}
\usepackage{geometry}
\geometry{margin=1in}

@@

    Please find our revised manuscript alongside the below response to the reviewers report. The authors would like to thank the editor, reviewer, and data editors for their thoughtful review. Please see below for responses to the report along with the accompanying updated manuscript, where changes are marked in \textcolor{blue}{\bf blue}.

@@

>>>>

\documentclass{letter}
\usepackage{xcolor}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{amsmath}

@@

    Please find our revised manuscript alongside the below response to the reviewers report. The authors would like to thank the editor, reviewer, and data editors for their thoughtful review, which has lead to a greatly improved manuscript.

@@

    \begin{response}
        {L580: I would conclude the discussion (or add to the conclusion) that, besides imposing constraints on the disc radial extend and j, the two studied mechanisms (disc breaking and self-gravity) are expected to lower the fraction of polar CBDs. If I understood correctly, large values of j and radially extended discs are unlikely to become polar (as a whole at least). Therefore, the statistical relevance/weight of this subgroup of discs should be less important at the overall polar CBD population level. This could be briefly commented at the end.}
        This is a great suggestion, however I think the overall effect is a bit different. High-$j$ disks have polar probabilities that are sensitive to initial inclination and insensitive to $e_{\rm b}$. Radially extended disks have long alignment timescales and may not evolve much within their lifetimes. Reducing these two populations (which should have significant overlap) would make $f_\text{polar}$ more sensitive to $e_{\rm b}$ and reduce the population of disks that end their lives outside of polar or coplanar alignments.
    \end{response}

    \begin{response}{
        L615: Unclear what "1/s" means. Below a second per calculation/timestep? Please specify.
    }
        We have clarified that this refers to the time to run a single simulation until it can be determined if the third body is undergoing circular precession or libration.
    \end{response}

    \begin{response}{
        L628: Sections (missing s).
    }
    This has been fixed.
    \end{response}
